Supplementary Information

### 2015-09-04 manuscript/supplement.tex
Main text files almost done - need to add by-TL back to SI, reference in main text

\subsection*{Appendix S1: Details of food web sources and selection}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        32    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
        33    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        34    & 3 & \cite{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
        35    & 3 & \cite{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
        36    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        37    & 3 & \cite{Clarke1967}    & marine & 41,02,49 N & Yes   &       \\
        38    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        39    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        40    & 3 & \cite{Harrison1962}  & terrestrial &       & No    & Generalised scheme \\
        41    & 3 & \cite{Parin1970}  & marine &       & No    & Could not locate original source \\
        42    & 3 & \cite{Vinogradov1978}  & marine &       & No    & Study site unclear \\
        43    & 3 & \cite{Rosenthal1974}    & marine & 32,57 N & Yes   &       \\
        44    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        45    & 3 & \cite{Tilly1968}    & stream & 41,22,55 N & Yes   &       \\
        46    & 3 & \cite{Patten1975}    & lake & 33,54 N & Yes   &       \\
        47    & 3 & \cite{Harris1980}    & lake &       & No    & Study site unclear \\
        48    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
        49    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
        50    & 3 & \cite{Nybakken1982}    & marine &       & No    & Generalised scheme \\
        51    & 3 & \cite{Dexter1947}    & marine & 42,38,56 N & Yes   &       \\
        52    & 3 & \cite{Paine1980a}    & marine & 58,27 N & Yes   &       \\
        53    & 3 & \cite{Paine1980a}    & marine & 48,19 - 48,37 N & Yes   &       \\
        54    & 3 & Unpublished  & marine &       & No    & Unpublished \\
        55    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
        56    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
        57    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        58    & 3 & \cite{Cohen1990}  & lake & 51,46 N & Yes   &       \\
        59    & 3 & \cite{Twomey1945}    & terrestrial & 40,09,47 N & Yes   &       \\
        60    & 3 & \cite{Rasmussen1941}    & terrestrial & 36,5-37 N & Yes   &       \\
        61    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        62    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        63    & 3 & \cite{Jones1950}     & stream & 52,25,08 N & Yes   &       \\
        64    & 3 & \cite{Cummins1966}    & stream & 41,39,33 N & Yes   &       \\
        65    & 3 & \cite{Tsuda1972}  & stream & 34,21,20 - 34,23,21 N & Yes   &       \\
        66    & 3 & \cite{Mann1972a}  & stream & 51,30 N & Yes   &       \\
        67    & 3 & \cite{Carlson1968}    & stream & 40,24,16 N & Yes   &       \\
        68    & 3 & \cite{Morgan1972}  & lake &       & No    & Could not locate original source \\
        69    & 3 & \cite{Cohen1990}  & estuary &       & No    & Could not locate original source \\
        70    & 3 & \cite{Kemp1977}    & estuary & 28,54,08 N & Yes   &       \\
        71    & 3 & \cite{Sorokin1972}  & lake & 48,00 N & Yes   &       \\
        72    & 3 & \cite{Baril1983}  & lake & 46,02 N & Yes   &       \\
        73    & 3 & \cite{Schiemer1979}  & lake &       & No    & Could not locate original source \\
        74    & 3 & \cite{Cohen1990} & marine & 34,15,00 S & Yes   &       \\
        75    & 3 & \cite{Pechlaner1972}  & lake & 47,11 N & Yes   &       \\
        76    & 3 & \cite{Schiemer1979}  & lake & 47,42 - 47,54 N & Yes   &       \\
        77    & 3 & \cite{Cohen1990}  & lake &       & No    & Could not locate original source \\
        78    & 3 & \cite{Burgis1972}  & lake & 0     & Yes   &       \\
        79    & 3 & \cite{Sarvala1974}  & lake &       & No    & Could not locate original source \\
        80    & 3 & \cite{Sarvala1974}  & lake &       & No    & Could not locate original source \\
        81    & 3 & \cite{Hatanaka1977}  & marine &       & No    & Could not locate original source \\
        82    & 3 & \cite{Cohen1990} & marine &       & No    & Could not locate original source \\
        83    & 3 & \cite{Cohen1990}  & lake &       & No    & Could not locate original source \\
        84    & 3 & \cite{Wilbur1972}    & lake & 42,28,42 N & Yes   &       \\
        85    & 3 & \cite{Mizuno1982}  & lake &       & No    & Could not locate original source \\
        86    & 3 & \cite{Hogetsu1979}  & marine & 34,36 - 35,38 N & Yes   &       \\
        87    & 3 & \cite{Bradstreet1982}  & terrestrial & 72,46,34.95 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

@@

\subsection*{Appendix S2: Forms of scaling relationships with species richness}

@@

\subsection*{Appendix S3: Testing for effects of sampling effort}

@@

    \begin{figure}[!h]
    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/LS_author.eps}}
    \caption{Estimates of the coefficients for scaling of link density with species richness
    in equation 5 (main text) do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the pseudovalues for each coefficient
    in the equation after the removal of all webs compiled by each author in the dataset. Authors
    who compiled only a single web were jackknifed as part of the by-web jackknife.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
    \label{LS_web}
    \end{figure}

@@

    \begin{figure}[!h]
    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/Gen_author.eps}}
    \caption{Estimates of the coefficients for scaling of generality with species richness
    (see equation 5, main text) do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the pseudovalues for each coefficient
    in the equation after the removal of all webs compiled by each author in the dataset. Authors
    who compiled only a single web were jackknifed as part of the by-web jackknife.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
    \label{Gen_web}
    \end{figure}

@@

    \begin{figure}[!h]
    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/Vul_author.eps}}
    \caption{Estimates of the coefficients for the scaling of vulnerability with species richness
    (see equation 5, main text) do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the pseudovalues for each coefficient
    in the equation after the removal of all webs compiled by each author in the dataset. Authors
    who compiled only a single web were jackknifed as part of the by-web jackknife.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
    \label{Vul_web}
    \end{figure}

@@

\subsection*{Appendix S4: Supplemental Figure}

\begin{figure}[!h]
\centerline{\includegraphics*[height=.75\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_observed.eps}}
\caption{Scaling relationships for link density, generality, 
and vulnerability relative to species richness and the proportions of basal resources (\% Basal),
intermediate consumers (\% Intermediate), top predators (\% Top), and species richness of a food web. 
For each relationship, we show observed values (white circles) and 
a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
any effects of habitat type or latitude (black line, N=196 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
observed values correcting for the effects of habitat type and latitude. }
\label{props_v_lat_obs}
\end{figure}

>>>>

\subsection*{Appendix S1: details of food web sources and selection}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        32    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
        33    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        34    & 3 & \cite{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
        35    & 3 & \cite{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
        36    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        37    & 3 & \cite{Clarke1967}    & marine & 41,02,49 N & Yes   &       \\
        38    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        39    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        40    & 3 & \cite{Harrison1962}  & terrestrial &       & No    & Generalised scheme \\
        41    & 3 & \cite{Parin1970}  & marine &       & No    & Could not locate original source \\
        42    & 3 & \cite{Vinogradov1978}  & marine &       & No    & Study site unclear \\
        43    & 3 & \cite{Rosenthal1974}    & marine & 32,57 N & Yes   &       \\
        44    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        45    & 3 & \cite{Tilly1968}    & stream & 41,22,55 N & Yes   &       \\
        46    & 3 & \cite{Patten1975}    & lake & 33,54 N & Yes   &       \\
        47    & 3 & \cite{Harris1980}    & lake &       & No    & Study site unclear \\
        48    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
        49    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
        50    & 3 & \cite{Nybakken1982}    & marine &       & No    & Generalised scheme \\
        51    & 3 & \cite{Dexter1947}    & marine & 42,38,56 N & Yes   &       \\
        52    & 3 & \cite{Paine1980a}    & marine & 58,27 N & Yes   &       \\
        53    & 3 & \cite{Paine1980a}    & marine & 48,19 - 48,37 N & Yes   &       \\
        54    & 3 & Unpublished  & marine &       & No    & Unpublished \\
        55    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
        56    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
        57    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        58    & 3 & \cite{Smirnov1961}  & lake & 51,46 N & Yes   &       \\
        59    & 3 & \cite{Twomey1945}    & terrestrial & 40,09,47 N & Yes   &       \\
        60    & 3 & \cite{Rasmussen1941}    & terrestrial & 36,5-37 N & Yes   &       \\
        61    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        62    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        63    & 3 & \cite{Jones1950}     & stream & 52,25,08 N & Yes   &       \\
        64    & 3 & \cite{Cummins1966}    & stream & 41,39,33 N & Yes   &       \\
        65    & 3 & \cite{Tsuda1972}  & stream & 34,21,20 - 34,23,21 N & Yes   &       \\
        66    & 3 & \cite{Mann1972a}  & stream & 51,30 N & Yes   &       \\
        67    & 3 & \cite{Carlson1968}    & stream & 40,24,16 N & Yes   &       \\
        68    & 3 & \cite{Morgan1972}  & lake &       & No    & Could not locate original source \\
        69    & 3 & \cite{Cohen1990}  & estuary &       & No    & Could not locate original source \\
        70    & 3 & \cite{Kemp1977}    & estuary & 28,54,08 N & Yes   &       \\
        71    & 3 & \cite{Sorokin1972}  & lake & 48,00 N & Yes   &       \\
        72    & 3 & \cite{Baril1983}  & lake & 46,02 N & Yes   &       \\
        73    & 3 & \cite{Schiemer1979}  & lake &       & No    & Could not locate original source \\
        74    & 3 & \cite{Brown1964} & marine & 34,15,00 S & Yes   &       \\
        75    & 3 & \cite{Pechlaner1972}  & lake & 47,11 N & Yes   &       \\
        76    & 3 & \cite{Schiemer1979}  & lake & 47,42 - 47,54 N & Yes   &       \\
        77    & 3 & \cite{Cohen1990}  & lake &       & No    & Could not locate original source \\
        78    & 3 & \cite{Burgis1972}  & lake & 0     & Yes   &       \\
        79    & 3 & \cite{Sarvala1974}  & lake &       & No    & Could not locate original source \\
        80    & 3 & \cite{Sarvala1974}  & lake &       & No    & Could not locate original source \\
        81    & 3 & \cite{Hatanaka1977}  & marine &       & No    & Could not locate original source \\
        82    & 3 & \cite{Cohen1990} & marine &       & No    & Could not locate original source \\
        83    & 3 & \cite{Cohen1990}  & lake &       & No    & Could not locate original source \\
        84    & 3 & \cite{Wilbur1972}    & lake & 42,28,42 N & Yes   &       \\
        85    & 3 & \cite{Mizuno1982}  & lake &       & No    & Could not locate original source \\
        86    & 3 & \cite{Hogetsu1979}  & marine & 34,36 - 35,38 N & Yes   &       \\
        87    & 3 & \cite{Bradstreet1982}  & terrestrial & 72,46,34.95 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

@@

\subsection*{Appendix S2: forms of scaling relationships with species richness}

@@

\subsection*{Appendix S3: testing for effects of sampling effort}

@@

    \begin{figure}[!h]
    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/LS_author.eps}}
    \caption{Estimates of the coefficients for scaling of link density with species richness
    in equation 5 (main text) do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the pseudovalues for each coefficient
    in the equation after the removal of all webs compiled by each author (or set of authors where
    multiple authors compiled identical sets of webs) in the dataset. Authors
    who compiled only a single web were jackknifed as part of the by-web jackknife.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line, and
    the number of webs removed in each jackknife is given in parentheses.}
    \label{LS_web}
    \end{figure}

@@

    \begin{figure}[!h]
    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/Gen_author.eps}}
    \caption{Estimates of the coefficients for scaling of generality with species richness
    (see equation 5, main text) do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the pseudovalues for each coefficient
    in the equation after the removal of all webs compiled by each author (or set of authors where
    multiple authors compiled identical sets of webs) in the dataset. Authors
    who compiled only a single web were jackknifed as part of the by-web jackknife.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line, and
    the number of webs removed in each jackknife is given in parentheses.}
    \label{Gen_web}
    \end{figure}

@@

    \begin{figure}[!h]
    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/Vul_author.eps}}
    \caption{Estimates of the coefficients for the scaling of vulnerability with species richness
    (see equation 5, main text) do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the pseudovalues for each coefficient
    in the equation after the removal of all webs compiled by each author (or set of authors where
    multiple authors compiled identical sets of webs) in the dataset. Authors
    who compiled only a single web were jackknifed as part of the by-web jackknife.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line, and
    the number of webs removed in each jackknife is given in parentheses.}
    \label{Vul_web}
    \end{figure}

@@

\subsection*{Appendix S5: supplemental figure}

\begin{figure}[!h]
\centerline{\includegraphics*[height=.75\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_observed.eps}}
\caption{Scaling relationships for link density, generality, 
and vulnerability relative to species richness of a food web. 
For each relationship, we show observed values (white circles) and 
a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
any effects of habitat type or latitude (black line, N=196 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
observed values correcting for the effects of habitat type and latitude. }
\label{props_v_lat_obs}
\end{figure}
